---
title: "Arm Strength Leaderboard"
description: "Which fielder's average arm strength is closest to their jersey number?"
---

```{r}
#| include: false
library(tidyverse)
library(gt)
library(gtExtras)
library(mlbplotR)

df <- read_csv("arm_strength_leaderboard.csv", show_col_types = FALSE) |>
  slice_head(n = 50) |>
  mutate(rank = row_number())
```

Which fielder's average arm strength is **closest to their jersey number**?

Covers **2020–present** (the full Statcast arm strength tracking era). Uses Statcast's qualified arm strength metric, which filters to a player's strongest throws by position to exclude non-competitive lobs:

- **1B** — average of top 1% of throws, minimum 100 throws
- **2B / SS / 3B** — average of top 5% of throws, minimum 75 throws
- **OF** — average of top 10% of throws, minimum 50 throws

Each player's best-matching season is shown.

```{r}
#| echo: false

df |>
  select(rank, fielder_name, jersey_number, arm_overall, diff,
         primary_position_name, season) |>
  gt() |>
  fmt_number(columns = c(arm_overall, diff), decimals = 1) |>
  gt_color_rows(
    columns = diff,
    palette = c("#FF1493", "#AAAAAA", "#4169E1"),
    domain  = c(0, max(df$diff))
  ) |>
  tab_style(
    style     = cell_text(style = "italic"),
    locations = cells_body(columns = rank)
  ) |>
  tab_style(
    style     = cell_text(weight = "bold", style = "italic"),
    locations = cells_body(columns = diff)
  ) |>
  cols_label(
    rank                  = "",
    fielder_name          = "Fielder",
    jersey_number         = "Jersey #",
    arm_overall           = "Arm Strength",
    diff                  = md("*Diff*"),
    primary_position_name = "Position",
    season                = "Season"
  ) |>
  tab_header(title = md("**Arm Strength Leaderboard**")) |>
  tab_source_note(
    source_note = md("Data: Baseball Savant (Statcast) · Updated June 2026")
  ) |>
  tab_options(
    table.background.color            = "white",
    table.border.top.style            = "hidden",
    table.border.bottom.style         = "hidden",
    column_labels.border.top.style    = "solid",
    column_labels.border.bottom.style = "solid",
    data_row.padding                  = px(4),
    source_notes.font.size            = 10,
    heading.align                     = "center",
    heading.title.font.size           = 18,
    heading.title.font.weight         = "bold"
  )
```

Full data: [arm_strength_leaderboard.csv](arm_strength_leaderboard.csv)
