---
title: "Pitcher Jersey Number Leaderboard"
description: "Which pitcher has thrown the most career pitches at exactly their jersey number's mph?"
---

```{r}
#| include: false
library(tidyverse)
library(gt)
library(gtExtras)
library(mlbplotR)

df <- read_csv("matching_speed_leaderboard.csv", show_col_types = FALSE) |>
  slice_head(n = 50) |>
  mutate(rank = row_number())
```

Which pitcher has thrown the most career pitches at **exactly their jersey number's mph** (rounded to nearest integer)?

Covers the full pitch tracking era — **2008–present** (PITCHf/x + Statcast). Jersey numbers are matched per season, so a pitcher who changed numbers mid-career only gets credit for pitches thrown at the speed matching their number that year.

```{r}
#| echo: false

df |>
  select(rank, player_name, jersey_number, matching_pitches) |>
  gt() |>
  fmt_integer(columns = matching_pitches) |>
  gt_color_rows(
    columns = matching_pitches,
    palette = c("#4169E1", "#AAAAAA", "#FF1493"),
    domain  = c(1, max(df$matching_pitches))
  ) |>
  tab_style(
    style     = cell_text(style = "italic"),
    locations = cells_body(columns = rank)
  ) |>
  tab_style(
    style     = cell_text(weight = "bold", style = "italic"),
    locations = cells_body(columns = matching_pitches)
  ) |>
  cols_label(
    rank             = "",
    player_name      = "Pitcher",
    jersey_number    = "Jersey #",
    matching_pitches = md("*Matching Pitches*")
  ) |>
  tab_header(title = md("**Pitcher Jersey Number Leaderboard**")) |>
  tab_source_note(
    source_note = md("Data: Baseball Savant (Statcast / PITCHf/x) · Updated June 2026")
  ) |>
  tab_options(
    table.background.color            = "white",
    table.border.top.style            = "hidden",
    table.border.bottom.style         = "hidden",
    column_labels.border.top.style    = "solid",
    column_labels.border.bottom.style = "solid",
    data_row.padding                  = px(4),
    source_notes.font.size            = 10,
    heading.align                     = "center",
    heading.title.font.size           = 18,
    heading.title.font.weight         = "bold"
  )
```

Full data: [matching_speed_leaderboard.csv](matching_speed_leaderboard.csv)
